timesliced_random_cell_selection

### 2018-11-23 src/timesliced_random_cell_selection.Rmd
check on env. correlate extraction (ca marche!)

    }
}
write.csv(background_all, "../output/bio/background_complete.csv", row.names = FALSE)
head(background_all_sp)
```

@@

>>>>

    }
}
write.csv(background_all_sp, "../output/bio/background_complete.csv", row.names = FALSE)
background_all <- as.data.frame(background_all_sp)
head(background_all_sp)
```

@@

```{r}
randchkxy <- randcheck[ , c("longitude_meters", "latitude_meters")] 
randchsp <- SpatialPointsDataFrame(coords = randchkxy, data = randcheck, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.

#row 1
temp_brick <-  brick("../data/env/netcdf/2002_03_chl.nc", lvar = 4)
t200203chl <- projectRaster(temp_brick, aea)
chls <- extract(x=t200203chl[[1]], y = randchsp[1, ]) 
chls
chld <- extract(x=t200203chl[[23]], y = randchsp[1, ]) 
chld 
temp_brick <-  brick("../data/env/netcdf/2002_03_mlp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
mlps <- extract(x=tempbrick[[1]], y = randchsp[1, ]) 
mlps
temp_brick <-  brick("../data/env/netcdf/2002_03_o2.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
o2s <- extract(x=tempbrick[[1]], y = randchsp[1, ]) 
o2s
o2d <- extract(x=tempbrick[[23]], y = randchsp[1, ]) 
o2d
temp_brick <-  brick("../data/env/netcdf/2002_03_salinity.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sals <- extract(x=tempbrick[[1]], y = randchsp[1, ]) 
sals
sald <- extract(x=tempbrick[[23]], y = randchsp[1, ]) 
sald
temp_brick <-  brick("../data/env/netcdf/2002_03_temp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
temps <- extract(x=tempbrick[[1]], y = randchsp[1, ]) 
temps
tempd <- extract(x=tempbrick[[23]], y = randchsp[1, ]) 
tempd
temp_brick <-  brick("../data/env/netcdf/2002_03_ssh.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sshs <- extract(x=tempbrick[[1]], y = randchsp[1, ]) 
sshs

#row 2
temp_brick <-  brick("../data/env/netcdf/2007_07_chl.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
tempbrick
chls <- extract(x=tempbrick[[1]], y = randchsp[2, ]) 
chls
chld <- extract(x=tempbrick[[13]], y = randchsp[2, ]) 
chld 
temp_brick <-  brick("../data/env/netcdf/2007_07_mlp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
mlps <- extract(x=tempbrick[[1]], y = randchsp[2, ]) 
mlps
temp_brick <-  brick("../data/env/netcdf/2007_07_o2.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
o2s <- extract(x=tempbrick[[1]], y = randchsp[2, ]) 
o2s
o2d <- extract(x=tempbrick[[13]], y = randchsp[2, ]) 
o2d
temp_brick <-  brick("../data/env/netcdf/2007_07_salinity.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sals <- extract(x=tempbrick[[1]], y = randchsp[2, ]) 
sals
sald <- extract(x=tempbrick[[13]], y = randchsp[2, ]) 
sald
temp_brick <-  brick("../data/env/netcdf/2007_07_temp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
temps <- extract(x=tempbrick[[1]], y = randchsp[2, ]) 
temps
tempd <- extract(x=tempbrick[[13]], y = randchsp[2, ]) 
tempd
temp_brick <-  brick("../data/env/netcdf/2007_07_ssh.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sshs <- extract(x=tempbrick[[1]], y = randchsp[2, ]) 
sshs

#row 3
temp_brick <-  brick("../data/env/netcdf/2011_08_chl.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
tempbrick
chls <- extract(x=tempbrick[[1]], y = randchsp[3, ]) 
chls
chld <- extract(x=tempbrick[[13]], y = randchsp[3, ]) 
chld 
temp_brick <-  brick("../data/env/netcdf/2011_08_mlp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
mlps <- extract(x=tempbrick[[1]], y = randchsp[3, ]) 
mlps
temp_brick <-  brick("../data/env/netcdf/2011_08_o2.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
o2s <- extract(x=tempbrick[[1]], y = randchsp[3, ]) 
o2s
o2d <- extract(x=tempbrick[[13]], y = randchsp[3, ]) 
o2d
temp_brick <-  brick("../data/env/netcdf/2011_08_salinity.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sals <- extract(x=tempbrick[[1]], y = randchsp[3, ]) 
sals
sald <- extract(x=tempbrick[[13]], y = randchsp[3, ]) 
sald
temp_brick <-  brick("../data/env/netcdf/2011_08_temp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
temps <- extract(x=tempbrick[[1]], y = randchsp[3, ]) 
temps
tempd <- extract(x=tempbrick[[13]], y = randchsp[3, ]) 
tempd
temp_brick <-  brick("../data/env/netcdf/2011_08_ssh.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sshs <- extract(x=tempbrick[[1]], y = randchsp[3, ]) 
sshs

#row 4
temp_brick <-  brick("../data/env/netcdf/2000_05_chl.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
tempbrick
chls <- extract(x=tempbrick[[1]], y = randchsp[4, ]) 
chls
chld <- extract(x=tempbrick[[2]], y = randchsp[4, ]) 
chld 
temp_brick <-  brick("../data/env/netcdf/2000_05_mlp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
mlps <- extract(x=tempbrick[[1]], y = randchsp[4, ]) 
mlps
temp_brick <-  brick("../data/env/netcdf/2000_05_o2.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
o2s <- extract(x=tempbrick[[1]], y = randchsp[4, ]) 
o2s
o2d <- extract(x=tempbrick[[2]], y = randchsp[4, ]) 
o2d
temp_brick <-  brick("../data/env/netcdf/2000_05_salinity.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sals <- extract(x=tempbrick[[1]], y = randchsp[4, ]) 
sals
sald <- extract(x=tempbrick[[2]], y = randchsp[4, ]) 
sald
temp_brick <-  brick("../data/env/netcdf/2000_05_temp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
temps <- extract(x=tempbrick[[1]], y = randchsp[4, ]) 
temps
tempd <- extract(x=tempbrick[[2]], y = randchsp[4, ]) 
tempd
temp_brick <-  brick("../data/env/netcdf/2000_05_ssh.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sshs <- extract(x=tempbrick[[1]], y = randchsp[4, ]) 
sshs

#row 5
temp_brick <-  brick("../data/env/netcdf/2012_06_chl.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
tempbrick
chls <- extract(x=tempbrick[[1]], y = randchsp[5, ]) 
chls
chld <- extract(x=tempbrick[[25]], y = randchsp[5, ]) 
chld 
temp_brick <-  brick("../data/env/netcdf/2012_06_mlp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
mlps <- extract(x=tempbrick[[1]], y = randchsp[5, ]) 
mlps
temp_brick <-  brick("../data/env/netcdf/2012_06_o2.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
o2s <- extract(x=tempbrick[[1]], y = randchsp[5, ]) 
o2s
o2d <- extract(x=tempbrick[[25]], y = randchsp[5, ]) 
o2d
temp_brick <-  brick("../data/env/netcdf/2012_06_salinity.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sals <- extract(x=tempbrick[[1]], y = randchsp[5, ]) 
sals
sald <- extract(x=tempbrick[[25]], y = randchsp[5, ]) 
sald
temp_brick <-  brick("../data/env/netcdf/2012_06_temp.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
temps <- extract(x=tempbrick[[1]], y = randchsp[5, ]) 
temps
tempd <- extract(x=tempbrick[[25]], y = randchsp[5, ]) 
tempd
temp_brick <-  brick("../data/env/netcdf/2012_06_ssh.nc", lvar = 4)
tempbrick <- projectRaster(temp_brick, aea)
sshs <- extract(x=tempbrick[[1]], y = randchsp[5, ]) 
sshs
```

it worked!
